|

### 2023-07-18 paper/01-introduction.Rmd
Changed "The paper" to "they"
removed "rate of"

The peer-reviewed literature on measuring the performance of football linemen (either offensive or defensive) is scant.
@AlamarGould2008 find an association between pass completion rate and successful pass blocking by offensive linemen.
The data for this study are collected for the first three weeks of the 2007 NFL season, manually recording whether a lineman holds a block and the time it took for quarterback to throw the football.
@AlamarGoldner2011 later follow up by using manually-tracked data for the 2010 season to estimate lineman performance for different team-positions instead of individual defenders (e.g., Chicago Bears' left tackle, Pittsburgh Steelers' center, etc.).
The paper uses survival analysis to model time in pocket and completion percentage for quarterbacks before proposing a measure for linemen's contribution to their team's passing in terms of yards gained.

>>>>

The peer-reviewed literature on measuring the performance of football linemen (either offensive or defensive) is scant.
@AlamarGould2008 find an association between pass completion rate and successful pass blocking by offensive linemen.
The data for this study are collected for the first three weeks of the 2007 NFL season, manually recording whether a lineman holds a block and the time it took for quarterback to throw the football.
@AlamarGoldner2011 later follow up by using manually-tracked data for the 2010 season to estimate lineman performance for different team-positions instead of individual defenders (e.g., Chicago Bears' left tackle, Pittsburgh Steelers' center, etc.).
They used survival analysis to model time in pocket and completion percentage for quarterbacks before proposing a measure for linemen's contribution to their team's passing in terms of yards gained.

### 2023-07-18 paper/03-methods.Rmd
Changed "The paper" to "they"
removed "rate of"

In materials science, strain [@callister2018materials] is the deformation of a material from stress, showing the rate of change in a material's length relative to its original length.
Formally, let $L(t)$ be the distance between any given two points of interest within a material at time $t$, and $L_0$ be the initial distance between those two points.
The strain for a material at time $t$ is defined as 
\begin{equation*}
\varepsilon(t)= \frac{L(t) - L_{0}}{L_{0}}.
\end{equation*}
Notice that this measure is unitless due to being a ratio of two quantities having the same dimension.

>>>>

In materials science, strain [@callister2018materials] is the deformation of a material from stress, showing the change in a material's length relative to its original length.
Formally, let $L(t)$ be the distance between any given two points of interest within a material at time $t$, and $L_0$ be the initial distance between those two points.
The strain for a material at time $t$ is defined as 
\begin{equation*}
\varepsilon(t)= \frac{L(t) - L_{0}}{L_{0}}.
\end{equation*}
Notice that this measure is unitless due to being a ratio of two quantities having the same dimension.
